---
title: "Introduction to alfred"
author: "Onno Kleen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{alfred}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

A quick introduction for downloading FRED and ALFRED data.

## Installation

You may install the last stable release via CRAN or the latest development version from github.

```{r, eval = FALSE}
install.packages("alfred")
# or
install.packages("devtools")
devtools::install_github("onnokleen/alfred")
```

## Usage

Downloading data is straightforward (for real-time data from ALFRED see below):

```{r}
# check internet connection, if FALSE all other chunks are not evaluated
InternetConnection <- curl::has_internet()

library(alfred)
if (InternetConnection) {
  df <- get_fred_series("INDPRO", "indpro")
}
```

The output is a data frame

```{r}
if (InternetConnection) {
  head(df)
}
```

This can be readily used, i.e. for plotting

```{r, fig.show = "hold"}
library(ggplot2)
if (InternetConnection) {
  ggplot(df) +
    geom_line(aes(x = date, y = indpro))
}
```

## Vintage data

When using get_alfred_series for downloading real-time data sets, there will be an additional column for the respective vintage dates.

```{r}
if (InternetConnection) {
df_vintages <-
  get_alfred_series("GDPC1", "rgdp",
                    observation_start = "2007-05-31",
                    realtime_start = "2008-05-31", realtime_end = "2009-03-30")
head(df_vintages)
}
```

Because of its output being a tidy data frame, it is easy to visualize revisions by

```{r, fig.show = "hold", fig.width = 6}
if (InternetConnection) {

ggplot(df_vintages) +
  geom_line(aes(x = date, y = rgdp, colour = as.factor(realtime_period))) +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    legend.position = "bottom"
  )
}
```

