---
title: "Introduction to alfred"
author: "Onno Kleen"
date: "`r Sys.Date()`"
#output: rmarkdown::html_vignette
output: pdf_document
vignette: >
  %\VignetteIndexEntry{alfred}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

A quick introduction for downloading FRED and ALFRED data.

## Installation

Right now, the devtools package is needed until I submitted the package to CRAN

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("onnokleen/alfred")
```

## Usage

Downloading data is straightforward (for real-time data from ALFRED see below):

```{r}
library(alfred)
df <- get_fred_series("INDPRO", "indpro")
```

The output is a data frame 

```{r}
df
```

This can be readily used, i.e. for plotting

```{r, fig.show = "hold"}
library(ggplot2)
ggplot(df) +
  geom_line(aes(x = date, y = indpro))
```

## Vintage data

When using get_alfred_series for downloading real-time data sets, there will be an additional column for the respective vintage dates.

```{r}
df_vintages <- 
  get_alfred_series("GDPC1", "rgdp",
                    observation_start = "2007-05-31",
                    real_time_start = "2008-05-31", real_time_end = "2009-03-30")
df_vintages
```

Because of its output being a tidy data frame, it is easy to visualise revisions by 

```{r, fig.show = "hold", fig.width = 6}
library(ggplot2)

ggplot(df_vintages) +
  geom_line(aes(x = date, y = rgdp, colour = as.factor(realtime_period))) +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    legend.position = "bottom"
  )
```
